---
title: "Data Cleaning & Preparation"
author: "T.J. Sullivan"
date: "`r Sys.Date()`"
output: github_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains all code relevant for preparing and cleaning the data relevant to this dissertation project. The end of this document will save the prepped & cleaned dataset for any subsequent analyses that need to be done. If anything needs to be changed or added to the dataset, this should be done here. 

First, let's load in the packages that we need to use for this. 

```{r, message = F, warning = F}
library(tidyverse)
library(sjmisc)
```

Let's pull in the initial data:

```{r}
orig <- readRDS("data/CCS_data_final_2021.01.10.Rds")
```

# Variables needed

## Demographics & covariates

This code creates a variable denoting race/ethnicity match at the couple level: 
```{r}
# This code will create a couple-level demographic variable that denotes match based on race/ethnicity and age. Variables term "match" indicate whether both partners share the same race/ethnicity identities.

# Separate out variables of interest into another dataframe, converts from long to wide to organize at the couple level. 
match <- dplyr::select(orig, CoupleID, ParticipantID, race_categ_spec) %>% 
  group_by(CoupleID) %>% 
  mutate(rownum = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(id_cols = CoupleID, names_from = rownum, names_prefix = "race_categ_spec_", values_from = race_categ_spec)

match <- match %>% 
  mutate(race_match = case_when(
    (race_categ_spec_1 == 'Non-Hispanic White' & race_categ_spec_2 == 'Non-Hispanic White') ~ 0, # both non-Hispanic White
    (race_categ_spec_1 == 'Non-Hispanic White') & (race_categ_spec_2 == 'Hispanic/White' | race_categ_spec_2 == 'Hispanic/Latinx' | race_categ_spec_2 == 'Black/African American' | race_categ_spec_2 == 'Asian' | race_categ_spec_2 == 'Native American or Alaska Native' | race_categ_spec_2 == 'Non-Hispanic Multiracial' | race_categ_spec_2 == 'Hispanic Black' | race_categ_spec_2 == 'Hispanic Asian' | race_categ_spec_2 == 'Hispanic Native Hawaiian/Other Pacific Islander' | race_categ_spec_2 == 'Hispanic Native American/Alaska Native' | race_categ_spec_2 == 'Hispanic Multiracial') ~ 1, # mixed (one non-Hispanic White, one BIPOC)
    (race_categ_spec_1 == 'Hispanic/White' | race_categ_spec_1 == 'Hispanic/Latinx' | race_categ_spec_1 == 'Black/African American' | race_categ_spec_1 == 'Asian' | race_categ_spec_1 == 'Native American or Alaska Native' | race_categ_spec_1 == 'Non-Hispanic Multiracial' | race_categ_spec_1 == 'Hispanic Black' | race_categ_spec_1 == 'Hispanic Asian' | race_categ_spec_1 == 'Hispanic Native Hawaiian/Other Pacific Islander' | race_categ_spec_1 == 'Hispanic Native American/Alaska Native' | race_categ_spec_1 == 'Hispanic Multiracial') & (race_categ_spec_2 == 'Non-Hispanic White') ~ 1, # mixed (one non-Hispanic White, one BIPOC)
    (race_categ_spec_1 == 'Hispanic/White' | race_categ_spec_1 == 'Hispanic/Latinx' | race_categ_spec_1 == 'Black/African American' | race_categ_spec_1 == 'Asian' | race_categ_spec_1 == 'Native American or Alaska Native' | race_categ_spec_1 == 'Non-Hispanic Multiracial' | race_categ_spec_1 == 'Hispanic Black' | race_categ_spec_1 == 'Hispanic Asian' | race_categ_spec_1 == 'Hispanic Native Hawaiian/Other Pacific Islander' | race_categ_spec_1 == 'Hispanic Native American/Alaska Native' | race_categ_spec_1 == 'Hispanic Multiracial') & (race_categ_spec_2 == 'Hispanic/White' | race_categ_spec_2 == 'Hispanic/Latinx' | race_categ_spec_2 == 'Black/African American' | race_categ_spec_2 == 'Asian' | race_categ_spec_2 == 'Native American or Alaska Native' | race_categ_spec_2 == 'Non-Hispanic Multiracial' | race_categ_spec_2 == 'Hispanic Black' | race_categ_spec_2 == 'Hispanic Asian' | race_categ_spec_2 == 'Hispanic Native Hawaiian/Other Pacific Islander' | race_categ_spec_2 == 'Hispanic Native American/Alaska Native' | race_categ_spec_2 == 'Hispanic Multiracial') ~ 2 # both BIPOC
  )) %>% 
  mutate(race_match = recode_factor(race_match,
                                    `0` = "Both non-Hispanic White",
                                    `1` = "Mixed (one partner non-Hispanic White, one BIPOC)",
                                    `2` = "Both BIPOC"))

# Isolate the variable, merge into larger dataset, reorder variables so race_match variable is with other race/ethnicity demo variables. 
match <- dplyr::select(match, CoupleID, race_match)
orig <- left_join(orig, match, by = c("CoupleID"))
rm(match)
```

Code race/ethnicity, sexual orientation, and gender identity into small variables for analyses:
```{r}
orig <- mutate(orig,
              race_dich = if_else(race_categ == 'Non-Hispanic White', 0, 1),
              race_dich = recode_factor(race_dich, 
                                        `0` = 'Non-Hispanic White', 
                                        `1` = 'BIPOC'),
              gender_three = case_when(GenderIdent == 'Woman' ~ 0,
                                       GenderIdent == 'Man' ~ 1,
                                       (GenderIdent == 'Transgender man (trans man)' | GenderIdent == 'Transgender woman (trans woman)' | GenderIdent == 'Gender non-conforming' | GenderIdent == 'Genderqueer' | GenderIdent == 'Non-binary' | GenderIdent == 'Other (specify)') ~ 2),
              gender_three = recode_factor(gender_three,
                                           `0` = 'Cis woman',
                                           `1` = 'Cis man',
                                           `2` = 'Gender diverse'),
              sxlorx_dich = if_else((SxlOrx == 'Gay' | SxlOrx == 'Lesbian'), 0, 1),
              sxlorx_dich = recode_factor(sxlorx_dich,
                                      `0` = 'Monosexual',
                                      `1` = 'Bi+'))
```

For any discrepant reports about relationship length or cohabitation length, average across the couple here:
```{r}
orig <- orig %>%
  group_by(CoupleID) %>% 
  mutate(rel_length_mths = mean(RelLength_Tot_Mos, na.rm = T),
         rel_length_yrs = mean(RelLength_Tot_Yrs, na.rm = T),
         cohab_length_mths = mean(CohabLength_Tot_Mos, na.rm = T) %>% ifelse(is.nan(.), NA, .),
         cohab_length_yrs = mean(CohabLength_Tot_Yrs, na.rm = T)  %>% ifelse(is.nan(.), NA, .)) %>% 
  ungroup() 
```


Select relevant variables in desired order:

```{r}
data <- orig %>% 
  select(CoupleID, ParticipantID, 
         # demographic variables
         Age, race_categ, race_categ_spec, race_dich, race_match, Educ, Income, Employment, SxlOrx, SxlOrx_Other_Text, SxlOrx_match, sxlorx_dich, GenderIdent, GenderIdent_Other_Text, GenderIdent_match, gender_three, Cohab, cohab_length_mths, cohab_length_yrs, rel_length_mths, rel_length_yrs, 
         # CSI-16
         starts_with("CSI"),
         # IHS
         starts_with("IHS"),
         # CTS2
         starts_with("CTS"),
         # life stressor discussion variables
         starts_with("PANAS_life"), StressorTopic, StressorTopic_sev, stressor_type_rc_life, GlobalCoping_rc_life, StressorTopic_choice,
         # disc stressor discussion variables
         starts_with("PANAS_disc"), DiscrimTopic, DiscrimTopic_sev, stressor_type_rc_disc, GlobalCoping_rc_disc, DiscrimTopic_choice,
         # discussion order
         DiscussionOrder
         ) %>% 
  # this takes out the old scores for the CTS2, see below
  select(-CTS_PsychPerp:-CTS_SGMspecVict_HR)
```

Quick step to aggregate the self-reported severity ratings for each discussion topic across the couple - in the raw format it's only with the individual whose topic was chosen. If needed, see main outcome analyses code for categorical coding of discussion topics beyond what was specifically written in by the participants.  

```{r}
data <- data %>% 
  group_by(CoupleID) %>% 
  mutate(StressorTopic_sev = mean(StressorTopic_sev, na.rm = T),
         DiscrimTopic_sev = mean(DiscrimTopic_sev, na.rm = T)) %>% 
  ungroup()
```

Note that couple 1057 is missing discrimination topic SR severity rating b/c this was probed by RA and they did not get a severity rating to write down (noted down below as well under missing data).

## CTS2 re-scoring

To have the CTS2 represent an estimate of the number of aggressive acts perpetrated/experienced in the last year (known as frequency scores), the Likert scale of 1-7 needs to be recoded such that responses reflect the midpoint of the acts represented by each response option. For example, 3-5x in the past year would be coded as a 4 acts (and NOT a 3 b/c it is the third option in the scale). Number 6 (More than 20 times in the past year) should be coded as 25 acts.  

There is some controversy of which scoring method is best for the CTS2 (for an example w/ psych aggression: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3576822/) Here, we're going to go with the original Straus et al. 1996 mid-point frequency scoring. This was not done in the original data cleaning syntax, so here is code for that to happen (step by step): 

```{r}
# set up data frame
data <- data %>% arrange(ParticipantID) %>% 
  group_by(CoupleID) %>% 
  mutate(rownum = row_number()) %>% 
  ungroup()

# recode midpoints & put these in new columns
data <- data %>% 
  mutate(across(CTS_1:CTS.SGM_50,
                ~ recode(.x, `3` = 4, `4` = 8, `5` = 15, `6` = 25),
                .names = "{col}_mid"))

# pull out items into separate dataframe to get highest report by either partner, arrange for easy visual check  
cts <- data %>% select(CoupleID, rownum, CTS_1_mid:CTS.SGM_50_mid) %>% 
  pivot_wider(id_cols = CoupleID, names_from = rownum, values_from = c(CTS_1_mid:CTS.SGM_50_mid)) %>% 
  # item 1 & 2: swore
  mutate(CTS_psych_swore_perp_p1 = if_else(CTS_1_mid_1 > CTS_2_mid_2, CTS_1_mid_1, CTS_2_mid_2),
         CTS_psych_swore_perp_p2 = if_else(CTS_1_mid_2 > CTS_2_mid_1, CTS_1_mid_2, CTS_2_mid_1)) %>% 
  relocate(c(CTS_psych_swore_perp_p1, CTS_psych_swore_perp_p2), .after = CTS_2_mid_2) %>% 
  # item 3 & 4: shouted
  mutate(CTS_psych_shout_perp_p1 = if_else(CTS_3_mid_1 > CTS_4_mid_2, CTS_3_mid_1, CTS_4_mid_2),
         CTS_psych_shout_perp_p2 = if_else(CTS_3_mid_2 > CTS_4_mid_1, CTS_3_mid_2, CTS_4_mid_1)) %>% 
  relocate(c(CTS_psych_shout_perp_p1, CTS_psych_shout_perp_p2), .after = CTS_4_mid_2) %>% 
  # item 5 & 6: stomped out of house
  mutate(CTS_psych_stomp_perp_p1 = if_else(CTS_5_mid_1 > CTS_6_mid_2, CTS_5_mid_1, CTS_6_mid_2),
         CTS_psych_stomp_perp_p2 = if_else(CTS_5_mid_2 > CTS_6_mid_1, CTS_5_mid_2, CTS_6_mid_1)) %>% 
  relocate(c(CTS_psych_stomp_perp_p1, CTS_psych_stomp_perp_p2), .after = CTS_6_mid_2) %>% 
  # item 7 & 8: spite
  mutate(CTS_psych_spite_perp_p1 = if_else(CTS_7_mid_1 > CTS_8_mid_2, CTS_7_mid_1, CTS_8_mid_2),
         CTS_psych_spite_perp_p2 = if_else(CTS_7_mid_2 > CTS_8_mid_1, CTS_7_mid_2, CTS_8_mid_1)) %>% 
  relocate(c(CTS_psych_spite_perp_p1, CTS_psych_spite_perp_p2), .after = CTS_8_mid_2) %>% 
  # item 9 & 10: insults
  mutate(CTS_psych_insult_perp_p1 = if_else(CTS_9_mid_1 > CTS_10_mid_2, CTS_9_mid_1, CTS_10_mid_2),
         CTS_psych_insult_perp_p2 = if_else(CTS_9_mid_2 > CTS_10_mid_1, CTS_9_mid_2, CTS_10_mid_1)) %>% 
  relocate(c(CTS_psych_insult_perp_p1, CTS_psych_insult_perp_p2), .after = CTS_10_mid_2) %>% 
  # item 11 & 12: destroy
  mutate(CTS_psych_destroy_perp_p1 = if_else(CTS_11_mid_1 > CTS_12_mid_2, CTS_11_mid_1, CTS_12_mid_2),
         CTS_psych_destroy_perp_p2 = if_else(CTS_11_mid_2 > CTS_12_mid_1, CTS_11_mid_2, CTS_12_mid_1)) %>% 
  relocate(c(CTS_psych_destroy_perp_p1, CTS_psych_destroy_perp_p2), .after = CTS_12_mid_2) %>% 
  # item 13 & 14: lousy
  mutate(CTS_psych_lousy_perp_p1 = if_else(CTS_13_mid_1 > CTS_14_mid_2, CTS_13_mid_1, CTS_14_mid_2),
         CTS_psych_lousy_perp_p2 = if_else(CTS_13_mid_2 > CTS_14_mid_1, CTS_13_mid_2, CTS_14_mid_1)) %>% 
  relocate(c(CTS_psych_lousy_perp_p1, CTS_psych_lousy_perp_p2), .after = CTS_14_mid_2) %>% 
  # item 15 & 16: threat
  mutate(CTS_psych_threat_perp_p1 = if_else(CTS_15_mid_1 > CTS_16_mid_2, CTS_15_mid_1, CTS_16_mid_2),
         CTS_psych_threat_perp_p2 = if_else(CTS_15_mid_2 > CTS_16_mid_1, CTS_15_mid_2, CTS_16_mid_1)) %>% 
  relocate(c(CTS_psych_threat_perp_p1, CTS_psych_threat_perp_p2), .after = CTS_16_mid_2) %>% 
  # item 17 & 18: threw smthg
  mutate(CTS_phys_threw_perp_p1 = if_else(CTS_17_mid_1 > CTS_18_mid_2, CTS_17_mid_1, CTS_18_mid_2),
         CTS_phys_threw_perp_p2 = if_else(CTS_17_mid_2 > CTS_18_mid_1, CTS_17_mid_2, CTS_18_mid_1)) %>% 
  relocate(c(CTS_phys_threw_perp_p1, CTS_phys_threw_perp_p2), .after = CTS_18_mid_2) %>% 
  # item 19 & 20: twisted arm or hair 
  mutate(CTS_phys_twist_perp_p1 = if_else(CTS_19_mid_1 > CTS_20_mid_2, CTS_19_mid_1, CTS_20_mid_2),
         CTS_phys_twist_perp_p2 = if_else(CTS_19_mid_2 > CTS_20_mid_1, CTS_19_mid_2, CTS_20_mid_1)) %>% 
  relocate(c(CTS_phys_twist_perp_p1, CTS_phys_twist_perp_p2), .after = CTS_20_mid_2) %>% 
  # item 21 & 22: pushed or shoved
  mutate(CTS_phys_push_perp_p1 = if_else(CTS_21_mid_1 > CTS_22_mid_2, CTS_21_mid_1, CTS_22_mid_2),
         CTS_phys_push_perp_p2 = if_else(CTS_21_mid_2 > CTS_22_mid_1, CTS_21_mid_2, CTS_22_mid_1)) %>% 
  relocate(c(CTS_phys_push_perp_p1, CTS_phys_push_perp_p2), .after = CTS_22_mid_2) %>% 
  # item 23 & 24: grabbed
  mutate(CTS_phys_grab_perp_p1 = if_else(CTS_23_mid_1 > CTS_24_mid_2, CTS_23_mid_1, CTS_24_mid_2),
         CTS_phys_grab_perp_p2 = if_else(CTS_23_mid_2 > CTS_24_mid_1, CTS_23_mid_2, CTS_24_mid_1)) %>% 
  relocate(c(CTS_phys_grab_perp_p1, CTS_phys_grab_perp_p2), .after = CTS_24_mid_2) %>%
  # item 25 & 26: slapped
  mutate(CTS_phys_slap_perp_p1 = if_else(CTS_25_mid_1 > CTS_26_mid_2, CTS_25_mid_1, CTS_26_mid_2),
         CTS_phys_slap_perp_p2 = if_else(CTS_25_mid_2 > CTS_26_mid_1, CTS_25_mid_2, CTS_26_mid_1)) %>% 
  relocate(c(CTS_phys_slap_perp_p1, CTS_phys_slap_perp_p2), .after = CTS_26_mid_2) %>% 
  # item 27 & 28: weapon
  mutate(CTS_phys_weapon_perp_p1 = if_else(CTS_27_mid_1 > CTS_28_mid_2, CTS_27_mid_1, CTS_28_mid_2),
         CTS_phys_weapon_perp_p2 = if_else(CTS_27_mid_2 > CTS_28_mid_1, CTS_27_mid_2, CTS_28_mid_1)) %>% 
  relocate(c(CTS_phys_weapon_perp_p1, CTS_phys_weapon_perp_p2), .after = CTS_28_mid_2) %>% 
  # item 29 & 30: punch 
  mutate(CTS_phys_punch_perp_p1 = if_else(CTS_29_mid_1 > CTS_30_mid_2, CTS_29_mid_1, CTS_30_mid_2),
         CTS_phys_punch_perp_p2 = if_else(CTS_29_mid_2 > CTS_30_mid_1, CTS_29_mid_2, CTS_30_mid_1)) %>% 
  relocate(c(CTS_phys_punch_perp_p1, CTS_phys_punch_perp_p2), .after = CTS_30_mid_2) %>% 
  # item 31 & 32: choke
  mutate(CTS_phys_choke_perp_p1 = if_else(CTS_31_mid_1 > CTS_32_mid_2, CTS_31_mid_1, CTS_32_mid_2),
         CTS_phys_choke_perp_p2 = if_else(CTS_31_mid_2 > CTS_32_mid_1, CTS_31_mid_2, CTS_32_mid_1)) %>% 
  relocate(c(CTS_phys_choke_perp_p1, CTS_phys_choke_perp_p2), .after = CTS_32_mid_2) %>% 
  # item 33 & 34: slam
  mutate(CTS_phys_slam_perp_p1 = if_else(CTS_33_mid_1 > CTS_34_mid_2, CTS_33_mid_1, CTS_34_mid_2),
         CTS_phys_slam_perp_p2 = if_else(CTS_33_mid_2 > CTS_34_mid_1, CTS_33_mid_2, CTS_34_mid_1)) %>% 
  relocate(c(CTS_phys_slam_perp_p1, CTS_phys_slam_perp_p2), .after = CTS_34_mid_2) %>% 
  # item 35 & 36: beat
  mutate(CTS_phys_beat_perp_p1 = if_else(CTS_35_mid_1 > CTS_36_mid_2, CTS_35_mid_1, CTS_36_mid_2),
         CTS_phys_beat_perp_p2 = if_else(CTS_35_mid_2 > CTS_36_mid_1, CTS_35_mid_2, CTS_36_mid_1)) %>% 
  relocate(c(CTS_phys_beat_perp_p1, CTS_phys_beat_perp_p2), .after = CTS_36_mid_2) %>% 
  # item 37 & 38: burned or scalded
  mutate(CTS_phys_burn_perp_p1 = if_else(CTS_37_mid_1 > CTS_38_mid_2, CTS_37_mid_1, CTS_38_mid_2),
         CTS_phys_burn_perp_p2 = if_else(CTS_37_mid_2 > CTS_38_mid_1, CTS_37_mid_2, CTS_38_mid_1)) %>% 
  relocate(c(CTS_phys_burn_perp_p1, CTS_phys_burn_perp_p2), .after = CTS_38_mid_2) %>% 
  # item 39 & 40: kicked
  mutate(CTS_phys_kick_perp_p1 = if_else(CTS_39_mid_1 > CTS_40_mid_2, CTS_39_mid_1, CTS_40_mid_2),
         CTS_phys_kick_perp_p2 = if_else(CTS_39_mid_2 > CTS_40_mid_1, CTS_39_mid_2, CTS_40_mid_1)) %>% 
  relocate(c(CTS_phys_kick_perp_p1, CTS_phys_kick_perp_p2), .after = CTS_40_mid_2) %>% 
  # item 41 & 42: threatout
  mutate(CTS_sgm_threatout_perp_p1 = if_else(CTS.SGM_41_mid_1 > CTS.SGM_42_mid_2, CTS.SGM_41_mid_1, CTS.SGM_42_mid_2),
         CTS_sgm_threatout_perp_p2 = if_else(CTS.SGM_41_mid_2 > CTS.SGM_42_mid_1, CTS.SGM_41_mid_2, CTS.SGM_42_mid_1)) %>% 
  relocate(c(CTS_sgm_threatout_perp_p1, CTS_sgm_threatout_perp_p2), .after = CTS.SGM_42_mid_2) %>% 
  # item 43 & 44: told how alone they would be without me
  mutate(CTS_sgm_alone_perp_p1 = if_else(CTS.SGM_43_mid_1 > CTS.SGM_44_mid_2, CTS.SGM_43_mid_1, CTS.SGM_44_mid_2),
         CTS_sgm_alone_perp_p2 = if_else(CTS.SGM_43_mid_2 > CTS.SGM_44_mid_1, CTS.SGM_43_mid_2, CTS.SGM_44_mid_1)) %>% 
  relocate(c(CTS_sgm_alone_perp_p1, CTS_sgm_alone_perp_p2), .after = CTS.SGM_44_mid_2) %>% 
  # item 45 & 46: rumor
  mutate(CTS_sgm_rumor_perp_p1 = if_else(CTS.SGM_45_mid_1 > CTS.SGM_46_mid_2, CTS.SGM_45_mid_1, CTS.SGM_46_mid_2),
         CTS_sgm_rumor_perp_p2 = if_else(CTS.SGM_45_mid_2 > CTS.SGM_46_mid_1, CTS.SGM_45_mid_2, CTS.SGM_46_mid_1)) %>% 
  relocate(c(CTS_sgm_rumor_perp_p1, CTS_sgm_rumor_perp_p2), .after = CTS.SGM_46_mid_2) %>% 
  # item 47 & 48: outed
  mutate(CTS_sgm_out_perp_p1 = if_else(CTS.SGM_47_mid_1 > CTS.SGM_48_mid_2, CTS.SGM_47_mid_1, CTS.SGM_48_mid_2),
         CTS_sgm_out_perp_p2 = if_else(CTS.SGM_47_mid_2 > CTS.SGM_48_mid_1, CTS.SGM_47_mid_2, CTS.SGM_48_mid_1)) %>% 
  relocate(c(CTS_sgm_out_perp_p1, CTS_sgm_out_perp_p2), .after = CTS.SGM_48_mid_2) %>% 
  # item 49 & 50: pda
  mutate(CTS_sgm_pda_perp_p1 = if_else(CTS.SGM_49_mid_1 > CTS.SGM_50_mid_2, CTS.SGM_49_mid_1, CTS.SGM_50_mid_2),
         CTS_sgm_pda_perp_p2 = if_else(CTS.SGM_49_mid_2 > CTS.SGM_50_mid_1, CTS.SGM_49_mid_2, CTS.SGM_50_mid_1)) %>% 
  relocate(c(CTS_sgm_pda_perp_p1, CTS_sgm_pda_perp_p2), .after = CTS.SGM_50_mid_2)

# only select the variables that contain the highest report of perpetration & restructure for merging back with data
cts <- cts %>% select(CoupleID, starts_with("CTS_psych"), starts_with("CTS_phys"), starts_with("CTS_sgm")) %>% 
  rename_with(function(x){gsub("_p1", ".partner_1", x)}) %>% 
  rename_with(function(x){gsub("_p2", ".partner_2", x)}) %>% 
  pivot_longer(cols = -CoupleID, names_to = c(".value", "rownum"), names_sep = ".partner_", names_transform = list(rownum = as.integer))

# merge highest report variables with main data 
data <- data %>% 
  left_join(cts, by = c("CoupleID", "rownum"))

# remove unneeded column 
rm(cts)
```

Now that we have the variables set up, create sum scores for frequency of IPV perpetrated over past-year:
```{r}
data <- data %>%  
  row_sums(starts_with("CTS_phys"), n = 0.7) %>% 
  rename(CTS_phys_perp_HR = rowsums)

data <- data %>% 
  row_sums(starts_with("CTS_psych"), n = 0.7) %>% 
  rename(CTS_psych_perp_HR = rowsums)

data <- data %>%
  row_sums(starts_with("CTS_sgm"), n = 0.7) %>% 
  rename(CTS_sgm_perp_HR = rowsums)
```

Finally, create variables marking prevalence (true = an act of aggression was reported):
```{r}
# individual-level prevalence
data <- data %>% 
  mutate(psych_ipv_prev = if_any(starts_with("CTS_psych"), ~ if_else(.x > 0, T, F)),
         phys_ipv_prev = if_any(starts_with("CTS_phys"), ~ if_else(.x > 0, T, F)),
         sgm_ipv_prev = if_any(starts_with("CTS_sgm"), ~ if_else(.x > 0, T, F))) 

# couple-level prevalence 
prev <- data %>% select(CoupleID, psych_ipv_prev:sgm_ipv_prev) %>% 
  group_by(CoupleID) %>% 
  mutate(num = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(id_cols = CoupleID, names_from = num, values_from = c(psych_ipv_prev:sgm_ipv_prev)) %>% 
  mutate(psych_ipv_prev_couple = case_when(
    (psych_ipv_prev_1 == F & psych_ipv_prev_2 == F) ~ 0,
    ((psych_ipv_prev_1 == F & psych_ipv_prev_2 == T) | (psych_ipv_prev_1 == T & psych_ipv_prev_2 == F)) ~ 1, 
    (psych_ipv_prev_1 == T & psych_ipv_prev_2 == T) ~ 2)) %>% 
  mutate(psych_ipv_prev_couple = recode_factor(psych_ipv_prev_couple, 
                                               `0` = "no violence",
                                               `1` = "unidirectional",
                                               `2` = "bidirectional")) %>%
  mutate(phys_ipv_prev_couple = case_when(
    (phys_ipv_prev_1 == F & phys_ipv_prev_2 == F) ~ 0,
    ((phys_ipv_prev_1 == F & phys_ipv_prev_2 == T) | (phys_ipv_prev_1 == T & phys_ipv_prev_2 == F)) ~ 1, 
    (phys_ipv_prev_1 == T & phys_ipv_prev_2 == T) ~ 2)) %>% 
  mutate(phys_ipv_prev_couple = recode_factor(phys_ipv_prev_couple, 
                                               `0` = "no violence",
                                               `1` = "unidirectional",
                                               `2` = "bidirectional")) %>%
  mutate(sgm_ipv_prev_couple = case_when(
    (sgm_ipv_prev_1 == F & sgm_ipv_prev_2 == F) ~ 0,
    ((sgm_ipv_prev_1 == F & sgm_ipv_prev_2 == T) | (sgm_ipv_prev_1 == T & sgm_ipv_prev_2 == F)) ~ 1, 
    (sgm_ipv_prev_1 == T & sgm_ipv_prev_2 == T) ~ 2)) %>% 
  mutate(sgm_ipv_prev_couple = recode_factor(sgm_ipv_prev_couple, 
                                               `0` = "no violence",
                                               `1` = "unidirectional",
                                               `2` = "bidirectional")) %>%
  select(CoupleID, psych_ipv_prev_couple:sgm_ipv_prev_couple)

data <- data %>% left_join(prev, by = "CoupleID") 

rm(prev)
```

# Prior discussion of discussion topics

For the original publication of this project, we did some by-hand coding of whether the topics chosen for discussions were previously discussed between partners. That was the case for the majority of the conversations. This file is saved under "CCS_data_prior_discussion" under the "Data" folder - we'll go ahead and pull that here and use that variable to be merged into the main dataframe here. 

```{r}
priordisc <- readRDS("data/CCS_data_prior_discussion.Rds")

data <- data |> 
  left_join(priordisc, by = "CoupleID")

rm(priordisc)
```


# Missing data 

This section contains code to mark who is missing data on each of the key variables of interest for analyses. 

## IHS 

There are no missing responses on the IHS: 
```{r}
data <- data %>% mutate(missing_IHS = ifelse(is.na(IHS_mean), T, F))
data %>% filter(missing_IHS == T) %>% select(CoupleID, ParticipantID)
```

## CTS

We see that 4 people are missing responses on the CTS2, which is two couples. The same two couples: 1025 and 1128 are missing data on all subscales of the CTS2. This is 2.38% of the sample. 

Physical:
```{r}
data <- data %>% mutate(missing_CTSphys = ifelse(is.na(CTS_phys_perp_HR), T, F))
data %>% filter(missing_CTSphys == T) %>% select(CoupleID, ParticipantID)
```
Psychological:
```{r}
data <- data %>% mutate(missing_CTSpsych = ifelse(is.na(CTS_psych_perp_HR), T, F))
data %>% filter(missing_CTSpsych == T) %>% select(CoupleID, ParticipantID)
```

SGM-specific:
```{r}
data <- data %>% mutate(missing_CTSsgm = ifelse(is.na(CTS_sgm_perp_HR), T, F))
data %>% filter(missing_CTSsgm == T) %>% select(CoupleID, ParticipantID)
```

This leaves us with an analytic sample of 82 couples for Aim 2 analyses. 

## Discussions

Next, we have the two couples that did not complete the stressor discussions due to technical difficulties. We were unable to re-schedule these participants. Therefore, they should be excluded from Aim 2 and Aim 3 analyses. This is couple 1054 and 1138.  

## PANAS

There are 3 couples who do not have PANAS data. Two of these are the ones who did not complete the discussions. Records confirmed that couple 1021 did not have the PANAS due to a technical error. 

Life stressor discussion:

```{r}
data <- data %>% mutate(missing_PANASlife = ifelse(is.na(PANAS_life_neg), T, F))
data %>% filter(missing_PANASlife == T) %>% select(CoupleID, ParticipantID)
```

Discrimination stressor discussion:
```{r}
data <- data %>% mutate(missing_PANASdisc = ifelse(is.na(PANAS_disc_neg), T, F))
data %>% filter(missing_PANASdisc == T) %>% select(CoupleID, ParticipantID)
```

Of note, there were 2 participants who were missing just 1 item on the PANAS after the life stressor discussion (PTID 192 for item 4 and PTID 243 for item 18)
```{r}
data %>% select(CoupleID, ParticipantID, PANAS_life_neg, c("PANAS_life_2", "PANAS_life_4", "PANAS_life_6", "PANAS_life_7", "PANAS_life_8", "PANAS_life_11", "PANAS_life_13", "PANAS_life_15", "PANAS_life_18", "PANAS_life_20")) %>% 
  filter(if_any(.fns = ~ is.na(.x))) %>% 
  # filter out couples that did not have PANAS
  filter(CoupleID != 1021 & CoupleID != 1054 & CoupleID != 1138)
```

Because we used sum scores, we went ahead and imputed these responses as 1, which was the mode for both participants here. 
```{r}
# replace values
data <- data %>% 
  mutate(PANAS_life_4 = ifelse(ParticipantID == 192, 1, PANAS_life_4),
         PANAS_life_18 = ifelse(ParticipantID == 243, 1, PANAS_life_18)) 

# recalculate sum totals
data$PANAS_life_neg <- rowSums(data[c("PANAS_life_2", "PANAS_life_4", "PANAS_life_6", "PANAS_life_7", "PANAS_life_8", "PANAS_life_11", "PANAS_life_13", "PANAS_life_15", "PANAS_life_18", "PANAS_life_20")], na.rm = TRUE)

# above code sets missing sums to 0, so this recodes couples with missing data to NA
data <- data %>% mutate(PANAS_life_neg = ifelse((CoupleID == 1021 | CoupleID == 1054 | CoupleID == 1138), NA_real_, PANAS_life_neg))
```

## CSI

No missing data on the CSI covariate. 
```{r}
data <- data %>% mutate(missing_CSI = ifelse(is.na(CSI_sum), T, F))
data %>% filter(missing_CSI == T) %>% select(CoupleID, ParticipantID)
```

## Global DC during discussions 

7 couples did not have global dyadic coping data for the life stressor discussion. 2 of these are the ones that did not complete any discussions.

```{r}
data <- data %>% mutate(missing_GlobalDClife = ifelse(is.na(GlobalCoping_rc_life), T, F))
data %>% filter(missing_GlobalDClife == T) %>% select(CoupleID, ParticipantID)
```
There was only 1 additional couples who had missing global dyadic coping data for the discrimination stressor discussions:

```{r}
data <- data %>% mutate(missing_GlobalDCdisc = ifelse(is.na(GlobalCoping_rc_disc), T, F))
data %>% filter(missing_GlobalDClife != T & missing_GlobalDCdisc == T) %>% select(CoupleID, ParticipantID)
```

## Discussion topic severity

There is one couple - 1057 - that had missing data on the self-reported discrimination topic severity because this was not collected by the RA when they probed about discussion topics to list. 

Life stressor severity: 
```{r}
data %>% select(CoupleID, ParticipantID, StressorTopic_sev) %>% filter(is.na(StressorTopic_sev)) %>% select(CoupleID, ParticipantID)
```

Discrimination stressor severity:
```{r}
data %>% select(CoupleID, ParticipantID, DiscrimTopic_sev) %>% filter(is.na(DiscrimTopic_sev)) %>% select(CoupleID, ParticipantID)
```

Let's take a look at the observed stressor expression severity rating (on a similar scale). 
```{r}
orig %>% filter(CoupleID == 1057) %>% select(CoupleID, ParticipantID, StressExpSev_rc_disc, DiscrimTopic_choice)
```

And then the mean of the self-reported discrimination stressor topic severity ratings. 

```{r}
mean(data$DiscrimTopic_sev, na.rm = T)
```

Both are at a 3, so let's go ahead and impute that value in for Couple 1057. We now see there is no missing data for that variable. 

```{r}
data <- data %>% mutate(DiscrimTopic_sev = ifelse(CoupleID == 1057, 3, DiscrimTopic_sev))

data %>% select(CoupleID, ParticipantID, DiscrimTopic_sev) %>% filter(is.na(DiscrimTopic_sev))
```

N for Aim 1 analyses is 82 couples (n = 164 individuals):
```{r}
data %>% 
  # 2 couples excluded 
  filter(missing_CTSphys == F) %>%
  filter(missing_CTSpsych == F) %>% 
  filter(missing_CTSsgm == F) 
```

N for Aim 2 analyses is 79 (n = 158 individs). 
```{r}
data %>% 
  # 2 couples excluded 
  filter(missing_CTSphys == F) %>%
  filter(missing_CTSpsych == F) %>% 
  filter(missing_CTSsgm == F) %>% 
  # 2 couples excluded 
  filter(CoupleID != 1054 | CoupleID != 1138) %>% 
  # 1 couple excluded
  filter(missing_PANASlife == F) %>%
  filter(missing_PANASdisc == F)
```

N for analyses with covariates is 72 couples (n = 144 individs):
```{r}
data %>% 
  # 2 couples excluded 
  filter(missing_CTSphys == F) %>%
  filter(missing_CTSpsych == F) %>% 
  filter(missing_CTSsgm == F) %>% 
  # 2 couples excluded 
  filter(CoupleID != 1054 | CoupleID != 1138) %>% 
  # 1 couple excluded
  filter(missing_PANASlife == F) %>%
  filter(missing_PANASdisc == F) %>% 
  # 5 couples excluded
  filter(missing_GlobalDClife == F) %>% 
  # 1 couple excluded 
  filter(missing_GlobalDCdisc == F) %>% 
  # 1 additional couple excluded b/c one partner did not report on race/ethnicity
  filter(CoupleID != 1083)
```

# Saving data file for analyses

Finally, let's save the data in a file. 

```{r}
saveRDS(data, file = "data/CCS_data_cleaned.rds")
```


